Dispersion of short waves riding on longer waves

### 2024-05-23 paper/paper.tex
Frequency modulation 2-panel
Start working on scale analysis

@@

\begin{equation}
\label{eq:effective_gravity}
\widetilde{g}(\psi) = g \left[
  1 - \varepsilon_L e^{\varepsilon_L \cos{\psi}} \left(
    \cos{\psi} + \varepsilon_L \sin^2{\psi}
  \right)
\right]
\end{equation}
The first-order term in $a_L k_L$ is in phase with the long-wave elevation,
so the apparent gravity of the short waves is increased at the long-wave crests
and decreased in the troughs.
The second-order term in $a_L k_L$ is positive-definite and phase-shifted by
$\pi/2$ relative to the crests.
The second-order term thus increases the apparent gravity on the front and rear
faces of the long wave (Fig. \ref{fig:apparent_gravity}).

@@

\begin{figure}[h]
\label{fig:frequency_modulation}
\centering
\includegraphics[width=\textwidth]{figures/fig_frequency_modulation.png}
\caption{
  Relative change in short-wave frequency due to the presence of longer
  waves, for four different values of long-wave steepness.
}
\end{figure}

@@

>>>>

TODO amplitude modulation;

@@

\begin{equation}
\label{eq:effective_gravity}
\widetilde{g}(\psi) = g + \dfrac{\partial W}{\partial t} = g \left[
  1 - \varepsilon_L e^{\varepsilon_L \cos{\psi}} \left(
    \cos{\psi} - \varepsilon_L \sin^2{\psi}
  \right)
\right]
\end{equation}
The first-order term in $a_L k_L$ is in phase with the long-wave elevation,
so the apparent gravity of the short waves is increased at the long-wave crests
and decreased in the troughs.
The second-order term in $a_L k_L$ is positive-definite and phase-shifted by
$\pi/2$ relative to the crests.
The second-order term thus increases the apparent gravity on the front and rear
faces of the long wave (Fig. \ref{fig:apparent_gravity}).

@@

\begin{figure}[h]
\label{fig:frequency_modulation}
\centering
\includegraphics[width=\textwidth]{figures/fig_frequency_modulation_2panel.png}
\caption{
  Relative change in short-wave frequency due to the presence of longer
  waves, for four different values of long-wave steepness.
}
\end{figure}

\subsection{Frequency and group speed modulation}

@@

We now proceed to integrate the full numerical solutions for the short-wave
wavenumber and action density in presence of long waves.
Equations (\ref{eq:wavenumber})-(\ref{eq:wave_action2}) are discretized using
2nd order central finite difference in space and integrated in time using the
4th order Runge-Kutta method \cite{butcher1996runge}.
Although the 2nd order central finite difference is not appropriate for many
numerical problems, in our case it is sufficient because it is conservative and
the fields that we compute derivatives of are smooth and continuous.
The space is divided into 100 grid points.

\subsection{Unstable growth in infinite long-wave trains}
\label{subsection:unstable_growth}

\begin{figure}[h]
\label{fig:frequency_modulation}
\centering
\includegraphics[width=\textwidth]{figures/fig_modulation_3panel_infinite_wave_train.png}
\caption{
  TODO
}
\end{figure}

\begin{figure}[h]
\label{fig:frequency_modulation}
\centering
\includegraphics[width=\textwidth]{figures/fig_modulation_3panel_linear_ramp.png}
\caption{
  TODO
}
\end{figure}

\subsection{Short-wave modulation by long-wave groups}
\label{subsection:wave_groups}

\begin{figure}[h]
\label{fig:frequency_modulation}
\centering
\includegraphics[width=\textwidth]{figures/fig_modulation_3panel_wave_group.png}
\caption{
  TODO
}
\end{figure}
